---
title: "Getting started with MosqEditR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with MosqEditR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

MosqEditR separates reusable scoring utilities from the manuscript analysis.

## Score three illustrative candidates

```{r}
library(MosqEditR)

z <- mosqedit_integrated_score(
  biology = c(0.99, 0.82, 0.61),
  pu = c(0.98, 0.75, 0.80),
  crispr = c(0.95, 0.91, 0.40)
)
z

mosqedit_rank(z$adjusted_score, c("A", "B", "C"))
```

## Inspect the frozen manuscript example

```{r}
head(mosqedit_example_candidates())
```

## Initialize a reproducible analysis workspace

```{r, eval=FALSE}
mosqedit_init("MosqEditR-analysis")
setwd("MosqEditR-analysis")
mosqedit_pipeline_steps()
mosqedit_install_pipeline_deps()
mosqedit_run_step("01")
```

The acquisition and modelling workflow has additional package requirements and may download public source data. Population-genomic integration is intentionally conditional on real site-level population metrics.
